Search for Spatially Extended \fermi-LAT Sources Using Two Years of Flight Data

### 2011-09-22 extended_catalog/paper/extended_catalog.tex
improvements

There will always be a small numerical discrepancy between the expected
photon distribution derived from a true point-like source and a very small
extended source due to numerical error in the convolution.  In most
situations, this error is insignificant.  But in particular for
very bright sources, this numerical error has the potential to bias the
test statistic for the extension test. Therefore, when calculating
\tsext, we compare the likelihood fitting the source with an extended
spatial model to the likelihood when the extension is
fixed to a very small value ($10^{-10}$ degrees in radius 
for a uniform surface brightness spatial model).

@@

For smaller and fainter extended sources, the differences in the PDF for
different spatial models lost in the noise and the LAT is not sensitive
to the detailed spatial structure of these sources.  Therefore, in our
search for extended sources we use only a radially-symmetric uniform
surface brightness as our spatial extension shape. Unless otherwise noted,
we quote the radius of the edge ($\sigma$) as the size of the source.
}

@@

We used a simulation setup similar to that described in
Section~\ref{monte_carlo_validation}, but instead of point-like sources
we simulated extended sources with a radially-symmetric uniform surface
brightness. Additionally, we simulated our sources over the two-year
time range included in 2FGL.  For each extension and spectral index,
we selected a flux range which bracketed $\tsext=16$ and performed an
extension test for $>100$ independent realizations of ten fluxes in
the range.  We calculated $\langle\tsext\rangle=16$ by fitting a line
to the flux and $\tsext$ values in the narrow range.

@@

We did this study first in the energy range from 1 \gev to 100 \gev by
simulating extended sources of flux $4\times10^{-9} \phflux$ integrated
from 1 \gev to 100 \gev with a power-law spectral model with
spectral index 2.  This flux was picked to be representative of the
new extended sourced that were discovered in the following analysis
when looking in the 1 \gev to 100 \gev energy range
(see Section~\ref{new_ext_srcs_section}).
We simulated these sources using a uniform surface brightness spatial
model with extensions varying
up to $1\degree$.  Figure~\ref{confusion_plot}a shows 
the distribution of \tsinc and \tsext as a
function of the simulated extension of the source
for 200 statistically independent simulations.

@@

Unless explicitly
mentioned, we used the same background model as 2FGL to represent the
Galactic diffuse, isotropic, and Earth limb emission.  To account for
possible residuals in the diffuse emission model, the galactic emission
was scaled by a power-law and the isotropic component's normalization
was left free.  
Unless explicitly mentioned,
we used all 2FGL sources within $15\degree$ of our source as our list
of background sources and we refit the spectral parameters of sources
within $2\degree$ of the source.

@@

\newtext{
As further validation of our extended source method for studying
spatially extended sources, we reanalyzed the twelve spatially extended
sources which were included in 2FGL \citep{second_cat}.  Even though
each of these sources required a dedicated analysis and these sources
were fit with a variety of spatial models, it is valuable to show that
these sources are significantly extended using our systematic extension
method and consistently assuming a radially-symmetric uniform surface
brightness for their spatial model.  On the other hand, for some of
these sources a uniform disk spatial model does not well describe the
observed extended emission and so the dedicated LAT publications give
a qualitatively better model of the source.

@@

Two nearby satellite galaxies of the Milky Way the Large Magellanic Cloud (LMC)
and the Small Magellanic
Cloud (SMC) were included in 2FGL as spatially extended sources \citep{lmc,smc}.  They were significantly
detected using photons with energies between
1 \gev and 100 \gev. Our
fit extension is comparable to the published result, but we note that
the previous LAT Collaboration publication on LMC used a more complicated two 2D Gaussian surface
brightness spatial model when fitting it (\citep{lmc}).

@@

% failed to detect vela x + cen a
Our analysis was unable to resolve Vela X which would have required first
removing the pulsed photons from the Vela pulsar which was beyond the
scope of this paper.  Our analysis also failed to detect a significant
extension for the Centaurus A Lobes because
the source's emission is significantly different from a uniform
radially-symmetric surface brightness \citep{cen_a_lat}.

Our analysis of these sources is summarized in
Table~\ref{known_extended_sources}.  This table includes the best fit
position and extension of these sources when fitting them 
with a radially-symmetric uniform surface brightness spatial model. It also
includes the best fit spectral parameters for each source.  The position
and extension of Vela X and the Centaurus A Lobes were taken from
\cite{velax,cen_a_lat} and are included in this list for completeness.

@@

\newtext{
For the LAT detected extended sources presented in this paper,
we developed two criteria for estimating the systematic error
on the extension of the source.
First, we estimated a systematic error due to
uncertainty in our knowledge of the LAT PSF.  
}
Before launch, the LAT PSF
was determined by detector simulations which were verified in accelerator
tests \citep{atwood_LAT_mission}. However, in-flight data revealed
a discrepancy above a few \gev in the PSF compared to the angular
distribution of photons from bright AGN \citep{lat_on_orbit_psf}.
Subsequently, the PSF was fit empirically to bright AGN and this
empirical parameterization is used in the P7\_V6 IRFs.  To account for
our uncertainty in our knowledge of the PSF, we refit our extended source
candidates using the pre-flight Monte Carlo representation of the PSF
and consider the difference in extension found using the two PSFs as a
systematic error on the extension of a source.  The same approach was used
in \cite{ic443}.  At high energies, we believe that our parameterization
of the PSF from bright AGN is substantially better than the Monte Carlo
representation of the PSF so this systematic error is conservative.

@@

\newtext{
It is not expected that this diffuse model is superior to the standard
LAT model obtained through an all-sky fit.  However, adding degrees of
freedom to the background model can remove likely spurious sources that
correlate with features in the Galactic diffuse emission.  Therefore,
this tests systematics that may be due to imperfect modeling of the
diffuse emission in the region. Nevertheless, this alternative diffuse
model does not test all systematics related to the diffuse emission model.
In particular, because the alternate model uses the same underlying gas
maps it is unable to asses systematics due to misidentified of local
diffuse structure due to lack lack of resolution of the underlying maps.
}

We do not expect the systematic error
due to uncertainties in the PSF to be correlated to the systematic
error due to uncertainty in the Galactic diffuse emission. Therefore,
the total systematic error on the extension of a source was obtained by
adding the two errors in quadrature.

@@

Now that we have demonstrated that we can analyze sources
previously known to be extended at \gev energies
(Section~\ref{validate_known})
and that we understand the statistical issues associated with
this analysis (Section~\ref{monte_carlo_validation} and~\ref{test_2lac_sources}),
we applied this method to search for new spatially extended \gev sources.

Ideally, we would have applied a completely blind search where we simply
fit the extension of each catalog source in the presence of all other 2FGL
sources to find a complete list of all the sources that are spatially
extended.  And as our test of AGN in Section~\ref{test_2lac_sources}
showed, at high galactic latitude where the source density is not as
great and the diffuse emission is less structured, this method works well.

This method is infeasible in the galactic plane where we
most likely expect to discover new spatially extended sources.  In the
galactic plane, the analysis becomes challenged by our imperfect model of
the diffuse emission and by issues related to source confusion.  
Finding sources on top of this emission
is difficult as was discussed in 1FGL
and 2FGL \citep{first_cat,second_cat} and we expect that finding
spatially extended sources be even more difficult.
The Monte
Carlo study on source confusion in Section~\ref{dual_localization_method}
showed that the overall likelihood would greatly increase when fitting
a spatially extended source as two point-like sources. So we expect that
most spatially extended LAT sources that are
currently modeled as point-like in 2FGL are surrounded by other 
point-like sources that representing
residual induced by not correctly modeling the sources' extension.
Furthermore, the position of other nearby sources in the region near
an extended source could be biased by not taking the extended
sources' extension into account.  Furthermore, 2FGL produced a
list of sources significant at energies above 100 \mev
whereas we are most sensitive to spatial extension at higher energies.
Therefore, we expect that when studying spatially extended sources
at higher energies our analysis would be complicated
by 2FGL sources not significant at higher energies and 2FGL sources
whose position was biased by the diffuse emission at lower energies.

To account for these issues,
we first produces a large list of
possibly extended sources employing a very liberal search criteria
and then refined the analysis of the promising candidates on a case by case basis.
Our strategy was to test all point-like 2FGL sources
for extension by assuming that they have a uniform radially-symmetric
uniform surface brightness
and that they have a power-law spectral model.
Although not all extended sources are
expected to have a shape very similar to a uniform surface brightness,
Section~\ref{compare_source_size} showed that for many spatially
extended sources the wide PSF of the LAT and limited statistics allows
for this to be a reasonable approximation.
Additionally,
our Monte Carlo studies (Section~\ref{monte_carlo_validation}
and~\ref{test_2lac_sources}) demonstrate that we can use this shape for a
statistically rigorous test. Because this spatial model only
adds one additional degree of freedom, this
test should be very sensitive to most spatially extended sources.
On the other hand, this spatial model could bias us against
finding extended sources which are not well described by uniform
emission such as certain shell-type supernova remnants.

Before testing for extension,
we automatically removed from the background model all other 2FGL
sources within 0\fdg5 of the source.  This value is somewhat arbitrary,
but was picked in hopes of finding extended sources with sizes on the
order of $\sim1\degree$ or smaller. On the other hand, by removing
these nearby background sources we expect to also incorrectly flag 
in our preliminary list point-like sources that are 
confused with
nearby sources.  To screen out obvious cases of source
confusion, we performed the dual localization procedure described in
Section~\ref{dual_localization_method} to compare the extended source
hypothesis to the hypothesis of two independent point-like sources.

@@

We also performed a second search for extended sources using only photons with
energies between 10 \gev and 100 \gev.  Although this approach tests the
same sources, it is complementary because the Galactic diffuse emission is
even less dominant above 10 \gev. Furthermore, source confusion becomes
less of a problem since most LAT sources are not significantly detected
at energies exclusively above 10 \gev. So we expected to be able to resolve
harder sources in more complicated regions by restricting our analysis
to higher energies. The $>10$ \gev analysis is especially beneficial
for regions near pulsars which are not significantly detected above
10 \gev. A similar procedure was used to detect HESS\,J1825$-$137 and
MSH\,15$-$52 with the LAT \citep{msh1552,fermi_hess_j1825}.

@@

Similarly, many of these sources were confused with nearby
point-like sources or influence by large-scale residuals in the
diffuse emission.  To help determine which of these fits represented
truly extended sourced and in which of these fits the extension was
influenced by source confusion and diffuse emission, we generated a
series of diagnostic plots.  For each candidate, we generated a map
of residual \ts by adding a new source of spectral index 2 into the
region at each pixel and finding the increase in likelihood when fitting
its flux. Figure~\ref{res_tsmaps} shows a residual \ts map around the
most significantly extended source IC443 when it is modeled both as a
point-like sources and an extended source.  The residual \ts map indicates
that the spatially extended model for IC443 is a significantly better
description of the observed photons and that there is no significant
residual in region after modeling the source as being spatially extended.
We also generated maps of the sum of all counts within a given distance of
the source and compared it to the model predictions assuming the emission
originated from a point-like source.  An example radial integral plot
is shown for the extended source IC443 in Figure~\ref{four_plots_ic443}.
For each source, we also made diffuse-emission-subtracted smoothed counts
maps (show for IC443 in Figure~\ref{four_plots_ic443}).

It was very clear by visually inspecting many of these plots that in many
cases our analysis was strongly influence by large-scale residual in the
diffuse emission and hence the extension measure was unreliable.  This was
especially true in our analysis of sources in the 1 \gev to 100 \gev
energy range.  An example of such a case is 2FGL\,J1856.2+0450c analyzed
in the 1 \gev to 100 \gev energy range. Figure~\ref{example_bad_fit}
shows a diffuse-emission-subtracted smoothed counts map with the best
fit extension of the source overlaid. There appears to be large-scale
residual in the diffuse emission in this region along the Galactic plane.
As a result, 2FGL\,J1856.2+0450c is fit to an extension of $\sim2\degree$
and the result is statistically significant with \tsext=45.4. However,
by looking at the residuals it is clear that this complicated region is
not well modeled. We manually discard sources like this.
% information came from
% /nfs/slac/g/ki/ki03/lande/extended_catalog/2FGL/v15/standard_analysis/spectral_emin_1000_v1/P72Y3047/v1/results_followup_P72Y3047.yaml
% (2FGL J1856.2+0450c = P72Y3047 for)

Because of these systematic issues, we only to selected candidates in
regions which seemed relatively simple or in regions where there was an
obvious spatially extended multiwavelength counterpart. Furthermore,
by assuming extended sources had a uniform spatial emission our
search was biased towards finding sources with this certain type of
morphology. Therefore, our search can not be expected to be complete
and it is likely that there are other spatially extended sources that
this method missed.

For each candidate that was not biased by neighboring point-like
sources or by large-scale residuals in the diffuse emission model, we
improved the model of the region by decided on a case by case basis which
background point-like sources should be kept.  We kept sources that we
believed represented physically distinct sources and we removed from the
model of the sky sources that we believed were included in 2FGL to account
for residual induced by not taking the extension of the extended source
into account and sources include in 2FGL to represent soft point-like
sources that were not significant at higher energies.  When deciding
which background sources to keep and which to remove, we used as much as possible
multiwavelenth information about possibly extended source counterparts
to help guild our choice. For each extended source presented in 
Section~\ref{new_ext_srcs_section}, we will describe any modification from 2FGL
of the background model that were required.

The best fit position of nearby point-like sources can be influenced by
the spatial model of a nearby extended source and vice versa.  Similarly,
the best fit position of nearby point-like sources in 2FGL can be biased
by systematic errors at lower energies.
Therefore, after selecting the list of sources, we had to iteratively
refit the position and spectrum of nearby background sources as well as
the position, extension, and spectrum of the analyzed spatially extended
sources until the overall fit had globally converged.  For each extended
source, we will describe these modifications.

After obtaining the overall best fit positions and extensions of all
of the sources in the region using \pointlike, we refit the spectral
parameters of the region using \gtlike.  Using \gtlike, we obtained a
second measure of \tsext.  We only consider a source to be extended when
both \pointlike and \gtlike agree that $\tsext>16$. 
We required also that $\tsext>16$ using the alternate diffuse
model presented in seciton~\ref{systematic_errors_on_extension}.
we then replaced the spatially extended source with two point-like
sources and refit their positions and spectrum and calculate \tsinc.
We only consider a source to be spatially extended, instead of being
the result of confusion of two point-like sources, if $\tsext>\tsinc$.
As was show in Section~\ref{dual_localization_method}, this test is
fairly powerful at removing situations in which the emission actually
originates from two distinct point-like sources instead of one spatially
extended source.  On the other hand, it is still possible that improved
observations could resolve additional structure or new sources that we are
currently not sensitive to. Considering the very complicated morphologies
of extended sources observed at other wavelengths and the high density
of possible sources that are expected to emit at \gev energies, it is
likely that in some of these regions further observations will resolve
that the emission is significantly more complicated than the simple
radially-symmetric uniform surface brightness model.

@@

\newtext{
Nine extended sources not included in 2FGL were found by our
extended source search. Two of these have been previously
studied in dedicated publications: RX\,J1713.7$-$3946 and Vela
Jr. \citep{rx_j1713_lat,vela_jr_lat}
Three of these sources were
found when using photons with energies between 1 \gev and 100 \gev and six
were found when using photons with energies between 10 \gev and 100 \gev.
For the sources found at energies above 10 \gev, we restrict our
analysis of these sources to higher energies because of the issues
of source confusion and diffuse emission modeling described in
section~\ref{extended_source_search_method}.
The spectral and spatial properties of these nine sources is summarized
in Table~\ref{new_ext_srcs_table}.  The results of our investigation of
systematic errors are presented in Table~\ref{alt_diff_model_results}.
This section compares the fit extension with an extended source hypothesis to the
fit assuming the emission originates from two independent point-like
sources. For these extended extended sources, $\tsext>\tsinc$ suggesting
that the \gev emission does not originate from multiple physically
distinct sources.  Table~\ref{alt_diff_model_results} also includes the
results of the extension fit using variations of the PSF and the galactic
diffuse model described in Section~\ref{systematic_errors_on_extension}.
There is good agreement between \tsext and the fit size using the standard
analysis, the alternative diffuse models, and the alternative PSF.
This suggests that the sources are robust against features in the diffuse
emission model and uncertainties in the angular resolution of the LAT.
}

@@

\newtext{
2FGL\,J0823.0$-$4246 was found by our search to be an extended source
candidate in the 10 \gev to 100 \gev energy range and is spatially
coincident with the SNR Puppis A.  Figure~\ref{1FGL_J0823.3-4248} shows
a counts map of this source and overlays and \rosat X-ray contours of
this source.  There are two nearby catalog sources 2FGL\,J0823.4$-$4305
and 2FGL\,J0821.0$-$4254 which are also coincident with the SNR but that
do not separate into multiple point-like components.  We concluded that
these two sources were included in 2FGL to account for residual induced
by not taking the extension of this extended source into account and
remvoed them from our model of the sky.

With this model, 2FGL\,J0823.0$-$4246 was found to have an extension of
$0\fdg37\pm0\fdg03_\stat\pm0\fdg02_\sys$ with an extension significance
of $\tsext=46.3$ using photons with energies between 1 \gev and 100 \gev.
This source was fit to $(l,b)=(260\fdg32,-3\fdg28)$ and is also coincident
with 1FGL\,J0823.3$-$4248.  Figure~\ref{snr_seds} shows the spectrum of
this source.

Puppis A has been studied in detail in radio (\cite{puppis_a_vla}, and
references therein) and  X-ray (\cite{rosat_puppis_a,suzaku_puppis_a},
and references therein).  The fit extension of 2FGL\,J0823.0$-$4246
match well its inferred size at \gev energies.  Puppis A's distance was
estimated at 2.2 kpc \citep{reynoso_1995,reynoso_2003} and leads to a 1
\gev to 100 \gev luminosity of $\sim 3\times 10^{34}$ ergs$\,\s^{-1}$.
No molecular clouds have been observed directly adjacent to Puppis A
\citep{co_eastern_puppis_a}, similar to the LAT detected Cyngus Loop SNR
\citep{cygnus_loop_lat}.  The luminosity of Puppis A is also smaller
than that of other SNRs believed to interact with molecular clouds
\citep{w51c,ic443,w44,w28,w49b_lat}.
}

@@

2FGL\,J1627.0$-$2425c was found by our search to
have an extension of $0\fdg41\pm0\fdg05_\stat\pm0\fdg02_\sys$ with
an extension significance of $\tsext=31.1$
using photons with energies between 1 \gev and 100 \gev.  The source
was fit to
$(l,b)=(353\fdg08, 16\fdg78)$ and is also coincident with 
1FGL\,J1628.6$-$2419c.  
Figure \ref{1FGL_J1628.6-2419c} shows a counts map of this source.

>>>>

There will always be a small numerical discrepancy between the expected
photon distribution derived from a true point-like source and a very small
extended source due to numerical error in the convolution.  In most
situations, this error is insignificant.  But in particular for
very bright sources, this numerical error has the potential to bias the
test statistic for the extension test. Therefore, when calculating
\tsext, we compare the likelihood fitting the source with an extended
spatial model to the likelihood when the extension is
fixed to a very small value ($10^{-10}$ degrees in radius 
for a uniform surface brightness profile).

@@

For smaller and fainter extended sources, the differences in the PDF for
different spatial models lost in the noise and the LAT is not sensitive
to the detailed spatial structure of these sources.  Therefore, in our
search for extended sources we use only a radially-symmetric uniform
surface brightness profile as our spatial extension shape. Unless otherwise noted,
we quote the radius of the edge ($\sigma$) as the size of the source.
}

@@

We used a simulation setup similar to that described in
Section~\ref{monte_carlo_validation}, but instead of point-like sources
we simulated extended sources with a radially-symmetric uniform surface
brightness profile. Additionally, we simulated our sources over the two-year
time range included in 2FGL.  For each extension and spectral index,
we selected a flux range which bracketed $\tsext=16$ and performed an
extension test for $>100$ independent realizations of ten fluxes in
the range.  We calculated $\langle\tsext\rangle=16$ by fitting a line
to the flux and $\tsext$ values in the narrow range.

@@

We did this study first in the energy range from 1 \gev to 100 \gev by
simulating extended sources of flux $4\times10^{-9} \phflux$ integrated
from 1 \gev to 100 \gev with a power-law spectral model with
spectral index 2.  This flux was picked to be representative of the
new extended sourced that were discovered in the following analysis
when looking in the 1 \gev to 100 \gev energy range
(see Section~\ref{new_ext_srcs_section}).
We simulated these sources using a uniform surface brightness profile
with extensions varying
up to $1\degree$.  Figure~\ref{confusion_plot}a shows 
the distribution of \tsinc and \tsext as a
function of the simulated extension of the source
for 200 statistically independent simulations.

@@

Unless explicitly
mentioned, we used the same background model as 2FGL to represent the
Galactic diffuse, isotropic, and Earth limb emission.  To account for
possible residuals in the diffuse emission model, the galactic emission
was scaled by a power-law and the isotropic component's normalization
was left free.  
Unless explicitly mentioned,
we used all 2FGL sources within $15\degree$ of our source as our list
of background sources and we refit the spectral parameters of all sources
within $2\degree$ of the source.

@@

\newtext{
As further validation of our extended source method for studying
spatially extended sources, we reanalyzed the twelve spatially extended
sources which were included in 2FGL \citep{second_cat}.  Even though
each of these sources required a dedicated analysis and they
were fit with a variety of spatial models, it is valuable to show that
these sources are significantly extended using our systematic extension
method that assumed a radially-symmetric uniform surface
brightness profile.  On the other hand, for some of
these sources a uniform disk spatial model does not well describe the
observed extended emission and so the dedicated LAT publications provides
a qualitatively better model these sources.

@@

Two nearby satellite galaxies of the Milky Way the Large Magellanic Cloud (LMC)
and the Small Magellanic
Cloud (SMC) were included in 2FGL as spatially extended sources \citep{lmc,smc}.  They were significantly
detected using photons with energies between
1 \gev and 100 \gev. Our
fit extension is comparable to the published result, but we note that
the previous LAT Collaboration publication on LMC used a more complicated two 2D Gaussian surface
brightness profile when fitting it (\citep{lmc}).

@@

% failed to detect vela x + cen a
Our analysis was unable to resolve Vela X which would have required first
removing the pulsed photons from the Vela pulsar which was beyond the
scope of this paper.  Our analysis also failed to detect a significant
extension for the Centaurus A Lobes because
the source's emission is significantly different from a uniform
radially-symmetric surface brightness profile \citep{cen_a_lat}.

Our analysis of these sources is summarized in
Table~\ref{known_extended_sources}.  This table includes the best fit
position and extension of these sources when fitting them 
with a radially-symmetric uniform surface brightness profile. It also
includes the best fit spectral parameters for each source.  The position
and extension of Vela X and the Centaurus A Lobes were taken from
\cite{velax,cen_a_lat} and are included in this list for completeness.

@@

\newtext{
For the extended sources presented in this paper,
we developed two criteria for estimating systematic errors
on the extension of the sources.
First, we estimated a systematic error due to
uncertainty in our knowledge of the LAT PSF.  
}
Before launch, the LAT PSF
was determined by detector simulations which were verified in accelerator
tests \citep{atwood_LAT_mission}. However, in-flight data revealed
a discrepancy above a few \gev in the PSF compared to the angular
distribution of photons from bright AGN \citep{lat_on_orbit_psf}.
Subsequently, the PSF was fit empirically to bright AGN and this
empirical parameterization is used in the P7\_V6 IRFs.  To account for
our uncertainty in our knowledge of the PSF, we refit our extended source
candidates using the pre-flight Monte Carlo representation of the PSF
and consider the difference in extension found using the two PSFs as a
systematic error on the extension of a source.  The same approach was used
in \cite{ic443}.  At high energies, we believe that our parameterization
of the PSF from bright AGN is substantially better than the Monte Carlo
representation of the PSF so this systematic error is conservative.

@@

\newtext{
It is not expected that this diffuse model is superior to the standard
LAT model obtained through an all-sky fit.  However, adding degrees of
freedom to the background model can remove likely spurious sources that
correlate with features in the Galactic diffuse emission.  Therefore,
this tests systematics that may be due to imperfect modeling of the
diffuse emission in the region. Nevertheless, this alternative diffuse
model does not test all systematics related to the diffuse emission model.
In particular, because the alternate model uses the same underlying gas
maps it is unable to asses systematics due to mischaracterization of local
diffuse structure due to lack lack of resolution of the underlying maps.
}

We do not expect the systematic error
due to uncertainties in the PSF to be correlated with the systematic
error due to uncertainty in the Galactic diffuse emission. Therefore,
the total systematic error on the extension of a source was obtained by
adding the two errors in quadrature.

@@

Now that we have demonstrated that we understand the statistical
issues associated with analyzing spatially extended sources
(Section~\ref{monte_carlo_validation} and~\ref{test_2lac_sources}) and
that our method can correctly analyze the extended sources included in
2FGL (Section~\ref{validate_known}), we apply this method to search for
new spatially extended \gev sources.

Ideally, we would apply a completely blind and uniform search that
tests the extension of each catalog source in the presence of all other
2FGL sources to find a complete list of all spatially extended sources.
As our test of AGN in Section~\ref{test_2lac_sources} showed, at high
galactic latitude where the source density is not as great and the
diffuse emission is less structured, this method works well.

But this is infeasible in the galactic plane where we most likely expect
to discover new spatially extended sources.  In the galactic plane,
this analysis is challenged by our imperfect model of the diffuse
emission and by issues related to source confusion.  The Monte Carlo
study in Section~\ref{dual_localization_method}
showed that the overall likelihood would greatly increase when fitting
a spatially extended source as two point-like sources so we expect
that spatially extended LAT sources are modeled in 2FGL as
multiple point-like sources. Furthermore, the position of other nearby sources
in the region near an extended source could be biased by not correctly
modeling the
sources' extension.  Furthermore, 2FGL produced a
list of sources significant at energies above 100 \mev whereas we are
most sensitive to spatial extension at higher energies.  Therefore,
we expect that at higher energies our analysis would be complicated
by 2FGL sources no longer significant and by 2FGL
sources whose position was biased by diffuse emission at lower energies.

To account for these issues, we first produces a large list of
possibly extended sources employing a very liberal search criteria
and then refined the analysis of the promising candidates on a case
by case basis.  Our strategy tested all point-like 2FGL sources for
extension assuming they had a uniform radially-symmetric uniform surface
brightness profile and a power-law spectral model.  Although not all
extended sources are expected to have a shape very similar to a uniform
surface brightness profile, Section~\ref{compare_source_size} showed that
for many spatially extended sources the wide PSF of the LAT and limited
statistics makes this a reasonable approximation.  Additionally, our Monte
Carlo study and AGN validation (Sections~\ref{monte_carlo_validation}
and~\ref{test_2lac_sources}) demonstrate that we can use this shape
for a statistically rigorous test. Because this spatial model only adds
one additional degree of freedom, this test should be very sensitive.
On the other hand, choosing this spatial model could bias us against
finding extended sources that are not well described by uniform emission
such as shell-type supernova remnants.

Before testing for extension,
we automatically removed from the background model all other 2FGL
sources within 0\fdg5 of the source.  This distance is somewhat arbitrary,
but was picked in hopes of finding extended sources with sizes on the
order of $\sim1\degree$ or smaller. On the other hand, by removing
these nearby background sources we expect to also incorrectly flag 
in our preliminary list point-like sources that are 
confused with
nearby sources.  To screen out obvious cases of source
confusion, we performed the dual localization procedure described in
Section~\ref{dual_localization_method} to compare the extended source
hypothesis to the hypothesis of two independent point-like sources.

@@

We also performed a second search for extended sources using only photons
with energies between 10 \gev and 100 \gev.  Although this approach
tests the same sources, it is complementary because the Galactic
diffuse emission is even less dominant above 10 \gev. Furthermore,
source confusion is less of a problem since many LAT sources are not
significantly detected at energies exclusively above 10 \gev. Therefore,
we expected to be able to resolve harder sources in more complicated
regions by restricting our analysis to higher energies.  The $>10$ \gev
analysis is especially beneficial for regions near pulsars which are
not significantly detected above 10 \gev. A similar procedure was used
to detect the spatial extension of HESS\,J1825$-$137 and MSH\,15$-$52
with the LAT \citep{msh1552,fermi_hess_j1825}.

@@

Similarly, many of these sources were confused with nearby
point-like sources or influence by large-scale residuals in the
diffuse emission.  To help determine which of these fits represented
truly extended sourced and in which of these fits the extension was
influenced by source confusion and diffuse emission, we generated a
series of diagnostic plots.  For each candidate, we generated a map
of the residual test statistic by adding a new source of spectral index 2 into the
region at each position and finding the increase in likelihood when fitting
its flux. Figure~\ref{res_tsmaps} shows this map around the
most significantly extended source IC443 when it is modeled both as a
point-like sources and an extended source.  The residual test statistic
map indicates
that the spatially extended model for IC443 is a significantly better
description of the observed photons and that there is not significant
residual in region after modeling the source as being spatially extended.
We also generated maps of the sum of all counts within a given distance of
the source and compared it to the model predictions assuming the emission
originated from a point-like source.  An example radial integral plot
is shown for the extended source IC443 in Figure~\ref{four_plots_ic443}.
For each source, we also made diffuse-emission-subtracted smoothed counts
maps (show for IC443 in Figure~\ref{four_plots_ic443}).

It was very clear by visual inspection that in many
cases our analysis was strongly influence by large-scale residual in the
diffuse emission and hence the extension measure was unreliable.  This was
especially true in our analysis of sources in the 1 \gev to 100 \gev
energy range.  An example of such a case is 2FGL\,J1856.2+0450c analyzed
in the 1 \gev to 100 \gev energy range. Figure~\ref{example_bad_fit}
shows a diffuse-emission-subtracted smoothed counts map around
this source with the best
fit extension of the source overlaid. There appears to be large-scale
residual in the diffuse emission in this region along the Galactic plane.
As a result, 2FGL\,J1856.2+0450c is fit to an extension of $\sim2\degree$
and the result is statistically significant with \tsext=45.4. However,
by looking at the residuals it is clear that this complicated region is
not well modeled. We manually discard sources like this.
% information came from
% /nfs/slac/g/ki/ki03/lande/extended_catalog/2FGL/v15/standard_analysis/spectral_emin_1000_v1/P72Y3047/v1/results_followup_P72Y3047.yaml
% (2FGL J1856.2+0450c = P72Y3047 for)

Because of these systematic issues, we only selected extended source
candidates in regions that did not appear dominated by these issues and
in regions where there was an obvious spatially extended multiwavelength
counterpart. Because of these systematic issues, this search can not be
expected to be complete and it is likely that there are other spatially
extended sources that this method missed.

For each candidate that was not biased by neighboring point-like
sources or by large-scale residuals in the diffuse emission model, we
improved the model of the region by decided on a case by case basis which
background point-like sources should be kept.  We kept sources that we
believed represented physically distinct sources and we removed from the
model of the sky sources that we believed were included in 2FGL to account
for residual induced by not modeling the extension of the source
and sources include in 2FGL to represent soft point-like
sources that were not significant at higher energies.  When deciding
which background sources to keep and which to remove, we used as much as possible
multiwavelength information about possibly extended source counterparts
to help guild our choice. For each extended source presented in 
Section~\ref{new_ext_srcs_section}, we will describe any modification from 2FGL
of the background model that were required.

The best fit position of nearby point-like sources can be influenced by
the spatial model of a nearby extended source and vice versa.  Similarly,
the best fit position of nearby point-like sources in 2FGL can be biased
by systematic errors at lower energies.
Therefore, after selecting the list of background sources, we iteratively
refit the position and spectrum of nearby background sources as well as
the position and extension of the analyzed spatially extended
sources until the overall fit globally converged.  For each extended
source, we will describe the position of any relocalized background
sources.

After obtaining the overall best fit positions and extensions of all
of the sources in the region using \pointlike, we refit the spectral
parameters of the region using \gtlike.  Using \gtlike, we obtained a
second measure of \tsext.  We only consider a source to be extended when
both \pointlike and \gtlike agree that $\tsext>16$. 
We further required that $\tsext>16$ using the alternate diffuse
model presented in section~\ref{systematic_errors_on_extension}.
We then replaced the spatially extended source with two point-like
sources and refit the position and spectrum of the
two point-like sources to calculate \tsinc.
We only consider a source to be spatially extended, instead of being
the result of confusion of two point-like sources, if $\tsext>\tsinc$.
As was show in Section~\ref{dual_localization_method}, this test is
fairly powerful at removing situations in which the emission actually
originates from two distinct point-like sources instead of one spatially
extended source.  On the other hand, it is still possible that improved
observations could resolve additional structure or new sources that we are
currently not sensitive to. Considering the very complicated morphologies
of extended sources observed at other wavelengths and the high density
of possible sources that are expected to emit at \gev energies, it is
likely that in some of these regions further observations will resolve
that the emission is significantly more complicated than the simple
radially-symmetric uniform surface brightness profile that we assume.

@@

\newtext{
Nine extended sources not included in 2FGL were found by our
extended source search. Two of these have been previously
studied in dedicated publications: RX\,J1713.7$-$3946 and Vela
Jr. \citep{rx_j1713_lat,vela_jr_lat}
Three of these sources were
found when using photons with energies between 1 \gev and 100 \gev and six
were found when using photons with energies between 10 \gev and 100 \gev.
For the sources found at energies above 10 \gev, we restrict our
analysis to higher energies because of the issues
of source confusion and diffuse emission modeling described in
section~\ref{extended_source_search_method}.
The spectral and spatial properties of these nine sources is summarized
in Table~\ref{new_ext_srcs_table} and the results of our investigation of
systematic errors are presented in Table~\ref{alt_diff_model_results}.
Table~\ref{alt_diff_model_results}
also
compares the likelihood assuming the source is spatially
extended to the likelihood assuming 
that the emission originates from two independent point-like
sources. For these new extended sources, $\tsext>\tsinc$ 
so we conclude that 
the \gev emission does not originate from two physically
distinct point-like sources (see Section~\ref{dual_localization_method}).  
Table~\ref{alt_diff_model_results} also includes the
results of the extension fit using variations of the PSF and the galactic
diffuse model described in Section~\ref{systematic_errors_on_extension}.
There is good agreement between \tsext and the fit size using the standard
analysis, the alternative diffuse models, and the alternative PSF.
This suggests that the sources are robust against features in the diffuse
emission model and uncertainties in the angular resolution of the LAT.
}

@@

\newtext{
2FGL\,J0823.0$-$4246 was found by our search to be an extended source
candidate in the 10 \gev to 100 \gev energy range and is spatially
coincident with the SNR Puppis A.  Figure~\ref{1FGL_J0823.3-4248} shows
a counts map of this source and overlays and \rosat X-ray contours of
Puppis A.  There are two nearby catalog sources 2FGL\,J0823.4$-$4305
and 2FGL\,J0821.0$-$4254 that are also coincident with the SNR but that
do not appear as separate point-like components.  We concluded that
these nearby point-like sources
were included in 2FGL to account for residual induced
by not modeling the extension of this source and
removed them from our model of the sky.
After removing these sources, 2FGL\,J0823.0$-$4246 was found to have an extension of
$0\fdg37\pm0\fdg03_\stat\pm0\fdg02_\sys$ with an extension significance
of $\tsext=46.3$.  Figure~\ref{snr_seds} shows the spectrum of
this source.

Puppis A has been studied in detail in radio (\cite{puppis_a_vla}, and
references therein) and  X-ray (\cite{rosat_puppis_a,suzaku_puppis_a},
and references therein).  The fit extension of 2FGL\,J0823.0$-$4246
matches well its inferred size at \gev energies.  Puppis A's distance was
estimated at 2.2 kpc \citep{reynoso_1995,reynoso_2003} and leads to a 1
\gev to 100 \gev luminosity of $\sim 3\times 10^{34}$ ergs$\,\s^{-1}$.
No molecular clouds have been observed directly adjacent to Puppis A
\citep{co_eastern_puppis_a}, similar to the LAT detected Cyngus Loop SNR
\citep{cygnus_loop_lat}.  The luminosity of Puppis A is also smaller
than that of other SNRs believed to interact with molecular clouds
\citep{w51c,ic443,w44,w28,w49b_lat}.
}

@@

2FGL\,J1627.0$-$2425c was found by our search to
have an extension of $0\fdg41\pm0\fdg05_\stat\pm0\fdg02_\sys$ with
an extension significance of $\tsext=31.1$
using photons with energies between 1 \gev and 100 \gev.  The source
Figure \ref{1FGL_J1628.6-2419c} shows a counts map of this source.
